---
title: "MA677_Assignment1"
author: "Maggie Sha"
date: "2/10/2021"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

# 1.Find m is in [69,73]

From the context, the significance level is 0.05. This indicates that it is acceptable
to have a 5% probability of incorrectly rejecting the true null hypothesis (Type I error).

Referring to Z-table, we have z = 1.65 or z = -1.65.

We also know that $\alpha(.6)$ is the upper tail of the a binomial distribution,
and $\alpha(.8)$ is the lower tail of a binomial distribution.

According to the equation: 
$$z =\frac{\hat{p}-p_o}{\sqrt{\frac{p_o(1-p_o)}{n}}}$$
We can get $$\hat{p} = 1.65 * sqrt(0.6*0.4) / 10 + 0.6 = 0.68$$
Thus $$ m = 0.68*n = 68$$

Similarly, 
$$\hat{p} = -1.65 * sqrt(0.8*0.2) / 10 + 0.8 = 0.73$$
$$ m = 0.73*n = 73$$
Thus, n is in [68,73]

## 2.Power Curve Plots
```{r}
f1 <- function(p){
  P1 <- 1 - pbinom(68,100,p)
}
f2 <- function(p) {
  P2 <- 1 - pbinom(73,100,p)
}
ggplot() +
  stat_function(fun = f1) +
  stat_function(fun = f2) +
  scale_x_continuous(limits = c(0.4, 1)) +
  scale_y_continuous(breaks= seq(0, 1, 0.1)) +
  annotate("rect", xmin = 0.6, xmax = 0.8, 
           ymin = 0.05, ymax = 0.95, alpha = 0.1, color = "black", fill = NA)
```

